---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## SARB Quarterly Bulletin Data

_<last updated on `r Sys.Date()`>_

This R package provides convenient access to the data that accompanies the South African Reserve Bank Quarterly Bulletin. Variables that are of the same frequency have been converted to `tibble` format and have been saved as `.RData` files. The names for each of these files is as follows:

- **sarb_annual.RData**
- **sarb_quarter.RData**
- **sarb_month.RData**
- **sarb_week.RData**
- **sarb_day.RData**

The column headers relate to each of the alpha-numeric codes that are used by the SARB. The first column is reserved for the date. The `lubridate` package was used for the date field where the first day of the year, quarter or month is used. In addition, the first Monday of the week is used from weekly data. The weekly data may include a few zeros that may have arisen on public holidays.

The most recent description file that is provided by the SARB has been saved is also included and an additional `.xlsx` version is included in the **desc** sub-folder. The layout is consistent with the way in which this data is provided.

## Installation

To install the repository the current data from GitLab:

```R
# install.packages("devtools")
devtools::install_gitlab("KevinKotze/sarbcurrent")
```

To install the repository the current data from GitHub:

```R
# install.packages("devtools")
devtools::install_github("KevinKotze/sarbcurrent")
```

## Usage

To view all of the data objects that are included in the package: 

```{r echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(sarbcurrent)
data(package = 'sarbcurrent')
```



```{r echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
sarb_quarter %>% 
  select(date, KBP6006D) %>% 
  tail()
```

## Historic real-time data vintages

Historic real-time data vintages, as described in the article by Dean Croushore and Tom Stark (2001), "A Real-Time Data Set for Macroeconomists", _Journal of Econometrics_, vol 105, pp. 111-30, may be accessed in a similar manner. For example, to access the dataset that was released in 2012q2, you should install the following package.

```R
devtools::install_gitlab("KevinKotze/sarb2012q2")
```

or 

```R
devtools::install_github("KevinKotze/sarb2012q2")
```

See <https://www.philadelphiafed.org/research-and-data/real-time-center/real-time-data/> for additional details on the real time dataset that is provided for the United States economy. 

## Disclaimer

Please note that this is not an official release of data and I'm in no way responsible for the results that may be produced using these data files. 
Researchers are encouraged to make use of the official data release that is available from the South African Reserve Bank. 
